### 2025-01-27 our_article/MCM_article/article_file.tex
论文思路大改

  \section{Appication of the Models}
    The process of model establishment has been thoroughly presented in the previous subsection. 
    In this subsection, we will discuss the application of the model.
    \subsection{Selection of Parameters}
      After reviewing the literature and aligning the parameters with their real-world significance, 
      we have determined a series of parameters. Due to the large number of parameters, 
      we will only present the table for the main ones:
        \caption{Parameters}
          $123$ & 123\\
        \label{tab:Parameters}
      All of the following models will apply these parameters.
      \subsection{Situation 1: No Agricultural Activities}
        This scenario will serve as a control group for familiarizing with the model. 
        We consider a situation without chemicals, sowing, or harvesting, 
        but with the migration of other species (since the migration of other species is an inevitable result of ecosystem maturation). 
        In this situation, we obtained the following population dynamics curve.
        From the figure, we can observe that under Scenario 1, the ecosystem develops normally, 
        but rice cannot survive in the long term, meaning the system cannot evolve into an agricultural ecosystem. 
        This indicates that the competitive ability of rice against weeds and its resistance to pests are relatively weak, 
        preventing it from sustainably existing in the ecosystem without human intervention. 
        This result is consistent with real-world observations and serves as the first validation of the model's accuracy.
      \subsection{Sutuation 2: Chemicals or Green Agriculture Solutions Used}
        In the discussion of Scenario 2, we consider a realistic situation. 
        A farmer has just cleared a forest to plant rice. 
        Initially, he uses chemicals such as herbicides and pesticides to suppress weeds and pests as the ecosystem gradually develops. 
        When the ecosystem matures to a certain extent, some species that had migrated from the forest ecosystem return, 
        enriching the food web of the farmland ecosystem. After further development, the ecosystem becomes relatively stable, 
        and the farmer stops using herbicides and pesticides, 
        instead turning to a green agriculture solution by introducing ducks and bats into the system.
        Specifically:
          \item The physiology of ducks prevents them from eating rice, but they can consume weeds and pests.
          \item Ducks are introduced two weeks after each sowing season and are harvested simultaneously with rice at the end of the season.
          \item Bats are introduced all at once and serve as both pollinators and insect predators.
        When the system evolved mature, the final food web of traditional farming mode and green farming mode are shown in 
        Figure \ref{fig:food_web_chem} and Figure \ref{fig:food_web_green} respectively.
            \includegraphics[height=6cm, keepaspectratio]{images/food_web_chem.pdf}
            \caption{Traditional Mode}
            \label{fig:food_web_chem}
              \includegraphics[height=6cm, keepaspectratio]{images/food_web.pdf} % 替换为你的第二张图片路径
              \caption{Green Mode}
              \label{fig:food_web_green}
        We will focus on comparing the succession of the ecosystem in the scenarios where humans use chemicals 
        (conventional scenario) and where humans use green agriculture solutions (target scenario). 
        In both cases, the ecosystem is unstable during the initial phase, 
        so we only show the dynamic behavior of the ecosystem after it reaches a stable state.

>>>>

  \section{Appication of the Models}
    The process of model establishment has been thoroughly presented in the previous subsection. 
    In this subsection, we will discuss the application of the model.
    \subsection{Selection of Parameters}
      After reviewing the literature and aligning the parameters with their real-world significance, 
      we have determined a series of parameters. Due to the large number of parameters, 
      we will only present the table for the main ones:
      \begin{table}[H]
        \centering
        \caption{Parameters}
        \begin{tabular}{cc}
          \toprule
          \rowcolor{customcolor!40} % 设置背景颜色
          Symbols & Description\\
          \midrule
          $123$ & 123\\
          \bottomrule
        \end{tabular}
        \label{tab:Parameters}
      \end{table}
      All of the following models will apply these parameters.
      \subsection{Scenarios Statement}
        \begin{table}[H]
          \centering
          \caption{Notations}
          \begin{tabular}{lccccccc}
            \toprule
            \rowcolor{customcolor!40} % 设置背景颜色
            conditions & Description\\
            \midrule
            Agro-Activities & Y & Y & Y & Y & Y & Y \\

            \bottomrule
          \end{tabular}
          \label{tab:Notations}
        \end{table}
      \subsection{Scenario 1: No Agricultural Activities}
        This scenario will serve as a control group for familiarizing with the model. 
        We consider a situation without chemicals, sowing, or harvesting, 
        but with the migration of other species (since the migration of other species is an inevitable result of ecosystem maturation). 
        In this situation, we obtained the following population dynamics curve.
        \begin{figure}[H]
        \end{figure}
        From the figure, we can observe that under Scenario 1, the ecosystem develops normally, 
        but rice cannot survive in the long term, meaning the system cannot evolve into an agricultural ecosystem. 
        This indicates that the competitive ability of rice against weeds and its resistance to pests are relatively weak, 
        preventing it from sustainably existing in the ecosystem without human intervention. 
        This result is consistent with real-world observations and serves as the first validation of the model's accuracy.
      \subsection{Scenario 2: Chemicals or Green Agriculture Solutions Used}
        In the discussion of Scenario 2, we consider a realistic situation. 
        A farmer has just cleared a forest to plant rice. 
        Initially, he uses chemicals such as herbicides and pesticides to suppress weeds and pests as the ecosystem gradually develops. 
        When the ecosystem matures to a certain extent, some species that had migrated from the forest ecosystem return, 
        enriching the food web of the farmland ecosystem. After further development, the ecosystem becomes relatively stable, 
        and the farmer stops using herbicides and pesticides, 
        instead turning to a green agriculture solution by introducing ducks and bats into the system.
        Specifically:
        \begin{itemize}
          \item The physiology of ducks prevents them from eating rice, but they can consume weeds and pests.
          \item Ducks are introduced two weeks after each sowing season and are harvested simultaneously with rice at the end of the season.
          \item Bats are introduced all at once and serve as both pollinators and insect predators.
        \end{itemize}
        When the system evolved mature, the final food web of traditional farming mode and green farming mode are shown in 
        Figure \ref{fig:food_web_chem} and Figure \ref{fig:food_web_green} respectively.
        \begin{figure}[H]
          \begin{minipage}[b]{0.45\linewidth}
            \centering
            \includegraphics[height=6cm, keepaspectratio]{images/food_web_chem.pdf}
            \caption{Traditional Mode}
            \label{fig:food_web_chem}
          \end{minipage}
          \hspace{0.05\linewidth}
          \begin{minipage}[b]{0.45\linewidth}
              \centering
              \includegraphics[height=6cm, keepaspectratio]{images/food_web.pdf} % 替换为你的第二张图片路径
              \caption{Green Mode}
              \label{fig:food_web_green}
          \end{minipage}
        \end{figure}
        We will focus on comparing the succession of the ecosystem in the scenarios where humans use chemicals 
        (conventional scenario) and where humans use green agriculture solutions (target scenario). 
        In both cases, the ecosystem is unstable during the initial phase, 
        so we only show the dynamic behavior of the ecosystem after it reaches a stable state.
